\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\usepackage{subfiles}
\usepackage{subfig}

\begin{document}
    \section{Time Series Forecasting}
        In this comprehensive section, we will delve deeper into the fascinating world of time series forecasting. Our exploration will encompass an extensive review of the various techniques available, allowing us to gain a comprehensive understanding of each approach's particularities and guiding principles. To ensure a well-rounded discussion, we will commence with an overview of traditional forecasting methods, exploring their strengths and limitations. Subsequently, we will progress to more advanced techniques that harness the power of deep learning, leveraging its capabilities for enhanced prediction accuracy. \par

        Throughout this section, we will enrich our understanding of these forecasting techniques by presenting a compelling case study. The case study will focus on data collected from Lawson female workers, comprising a diverse range of variables, including heart rate, movement patterns, and temperature. By utilizing this real-world dataset, we will illustrate how these forecasting methods can be effectively applied in practice, elucidating their practical implications and showcasing their performance on complex biosignal data. \par
        
        By integrating theoretical discussions, practical examples, and case studies, this section aims to equip readers with a holistic understanding of time series forecasting techniques. Whether you are a researcher, data scientist, or healthcare professional, this comprehensive exploration will empower you to confidently select and apply the most suitable forecasting approach for your specific problem domain, unlocking the potential to make accurate predictions and informed decisions based on biosignal time series data.\par

        \subfile{Subsections/traditional_techniques}
        \subfile{Subsections/deep_learning}

\end{document}